### 2020-04-28 manuscript/manuscript.rmd
reknit after fixing path

---
bibliography: manuscript.bib
csl: nature.csl
output:
  word_document: default
  pdf_document: default
  html_document: default
  github_document: default
---

@@

``` {r sensitive, fig.width=8, fig.height=8}
sensitive = read_tsv("/animal_root/data_processed/tables/sensitive.tsv")
Philippe2009 = sensitive %>% filter(Matrix == "Philippe2009_only_choanozoa" )
Philippe2009$Model = factor(Philippe2009$Model, levels=c("Poisson_CAT60" , "Poisson_CAT90","Poisson_CAT120","Poisson_CAT150","Poisson_CAT180"))
p1<-ggplot(Philippe2009, aes(Model))+
  geom_line(aes(y = `Ctenophora-sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `Ctenophora-sister` ), color=("#E69F00"))+
  geom_line(aes(y = `Porifera-sister`, colour = "Porifera-sister",group=2), color=("#009E73")) + geom_point(aes(y = `Porifera-sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Philippe2009_Choanozoa")

>>>>

---
bibliography: manuscript.bib
csl: nature.csl
output:
  pdf_document: default
  word_document: default
  html_document: default
  github_document: default
---

@@

``` {r sensitive, fig.width=8, fig.height=8}
sensitive = read_tsv("../data_processed/tables/sensitive.tsv")
Philippe2009 = sensitive %>% filter(Matrix == "Philippe2009_only_choanozoa" )
Philippe2009$Model = factor(Philippe2009$Model, levels=c("Poisson_CAT60" , "Poisson_CAT90","Poisson_CAT120","Poisson_CAT150","Poisson_CAT180"))
p1<-ggplot(Philippe2009, aes(Model))+
  geom_line(aes(y = `Ctenophora-sister`, colour = "Ctenophora-sister", group=1), color=("#E69F00")) + geom_point(aes(y = `Ctenophora-sister` ), color=("#E69F00"))+
  geom_line(aes(y = `Porifera-sister`, colour = "Porifera-sister",group=2), color=("#009E73")) + geom_point(aes(y = `Porifera-sister` ), color=("#009E73"))+
  scale_fill_manual(values=c("#E69F00", "#ebd196")) +
  theme_classic() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) +
  labs(x ="Number of CAT substitutional categories", y = "Support") + ggtitle("Philippe2009_Choanozoa")
